### 2019-10-22 thesis/txt/1-related-work.tex
data analysis, after many tries now in python notebooks with pandas

The structure of build logs
\begin{itemize}
  \item is \textbf{implicit}, as we do not have access to explicit structuring elements or an explicit structure description and computation is required to obtain the structure which is present.
  \item is \textbf{irregular}, as changes in the build process or execution environment might change it without notice.
  We observed this in the logs we collected for the \emph{Failing Build Log Data Set}, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
  You can see an example of this in Figure \ref{fig:log-4} and Figure \ref{fig:log-5}.
  \item is \textbf{partial}, some parts are highly structured by e.g. structure indicating special characters and others are unstructured, e.g. natural language text in error messages.
  \item can described with an \textbf{a-posteriori data guide} than an a-priori schema.
  There is no fixed specification on how build tools have to structure their output, more we afterwards extract structuring patterns in the produced output.
  \item has a \textbf{rapidly evolving} schema.
  Modifications in the build configuration change the tools involved in the build and therefore the composition of the build log.
\end{itemize}

>>>>

The structure of build logs
\begin{itemize}
  \item is \textbf{implicit}.
  We do not have access to explicit structuring elements or an explicit structure description.
  Computation is required to infer the present structure.
  \item is \textbf{irregular}.
  Changes in the build process or execution environment might change the structure of a build log without notice.
  We observed this in the logs we collected for the \emph{Failing Build Log Data Set}, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
  You can see an example of this in Figure \ref{fig:log-4} and Figure \ref{fig:log-5}.
  \item is \textbf{partial}, some parts are highly structured by e.g. structure indicating special characters and others are unstructured, e.g. natural language text in error messages.
  \item can described with an \textbf{a-posteriori data guide} than an a-priori schema.
  There is no fixed specification on how build tools have to structure their output, more we afterwards extract structuring patterns in the produced output.
  \item has a \textbf{rapidly evolving} schema.
  Modifications in the build configuration change the tools involved in the build and therefore the composition of the build log.
\end{itemize}
